% Abstract

\pdfbookmark[1]{Abstract}{Abstract} % Bookmark name visible in a PDF viewer
\thispagestyle{scrheadings}

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Abstract} % Abstract name

\noindent The objective of this report is to analyze the viability of the project «Radio Comem». It analyzes the projects primary objectives which are: language and technical education and the creation of identity for comem+. It also looks at the secondary objective or by-product of the project which are the podcasts being produced. These objectives are linked as they support each other.

\paragraph{} As the project has already started, this report incorporates many insights that have been gained while running Radio Comem. It then analyzes them from a marketing point of view, incorporates additional information and organizes the results in the given educational framework.

\paragraph{}Despite the educational nature of the report, it is still meant to serve as a base for future marketing decisions regarding Radio Comem.

\paragraph{}The conclusion of the report is, that there is enough demand in the department to run the project. Marketing should first and foremost be targeted at potential participants. In a first phase, the audience of the podcasts produced will consist mostly of people who have a direct link to the department. Later on, by the means of organic growth it is imaginable to market the podcasts to a larger audience.

\endgroup			

\vfill
